Dark matter halo concentrations with a bayesian approach

### 2014-09-30 paper/article.tex
added new plots

In Figure XXX we show the circular velocity profile for the same
concentrations as in Figure \ref{fig:profiles}.

@@

{\bf Cuantos pasos usa la cadena? De cuanto es el sigma en
los saltos de c en lca cadena?

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{vel_normalized.pdf}
\end{center}
\caption{Dimensionless velocity profiles as a function of the
  dimensionless radius for different concentration values.
    \label{fig:velocity}}
\end{figure}

In Figure \ref{fig:velocity} we show the circular velocity profile for the same
concentrations as in Figure \ref{fig:profiles}.

@@

{\bf Cuantos pasos usa la cadena? (50000) De cuanto es el sigma en
los saltos de c en lca cadena? (0.029)
